Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-13 tex/paper1/paper1.tex
edits to the paper

All these detections algorithms, and many detections in the literature
make either the explicit or implicit {\bf modeling} assumption that
the observed time-series consists of a background trend of some kind
and at least approximately Gaussian-distributed noise.  {\bf The aim
  of this paper is to investigate the nature of the Fourier power
  spectrum in regions of interest to study of the coronal seismology,
  thereby testing the assumption above}.  It is shown below, using
data from the Atmospheric Imaging Assembly (AIA,
\citealp{2012SoPh..275...17L}) on board the Solar Dynamics Observatory
(SDO, \citealp{2012SoPh..275....3P}), that time-series of coronal
emission may be better described by other models{\bf , based power-law
  power spectra that are actually observed} .  These models, {\bf
  based around \PL\ Fourier \PS}, have implications for the practice
of coronal seismology, and may be indicative of the nature of the
fundamental energy deposition that keeps the corona hot.

@@

Hence, the number of effectively independent pixels time-series must
be calculated. First, a pair of randomly chosen next-nearest neighbor
pixels are selected from the region.  Next nearest neighbor pixels are
chosen as close physical proximity is most likely to express the
strongest interdependence.  Next, the cross correlation $c(\tau)$
function between two randomly chosen next-nearest neighbor pixels is
calculated.  The cross correlation coefficient measures the linear
dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
lag {\bf times $\tau$.  This analysis assumes that the linear
  dependence as measured by the cross-correlation coefficient
  estimates the actual dependence between time-series.}

The cross correlation coefficient is used to define a coefficient of
independence between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  This
procedure is repeated 10,000 times.  For each value of $\rho$ found,
the effective number of pixels $N_{eff}$ is defined as
values is defined as
\begin{equation}\label{eqn:neff}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
where $\hat{\rho}$ is the arithmetic mean of the values of $\rho$ found.

>>>>

All these detections algorithms, and many detections in the literature
make either the explicit or implicit assumption that the observed
time-series consists of a background trend of some kind and
(approximately) Gaussian-distributed noise which must be taken in to
account in order to test for the presence of an oscillatiory signal.
{\bf The aim of this paper is to investigate the nature of the Fourier
  power spectrum in regions of interest to coronal seismology, to look
  for evidence that the above assumption is appropriate.  Data from
  the Atmospheric Imaging Assembly (AIA,
  \citealp{2012SoPh..275...17L}) on board the Solar Dynamics
  Observatory (SDO, \citealp{2012SoPh..275....3P}) is used.  It is
  shown that time-series of coronal emission have power-law power
  spectra, at least approximately.}  The \PL\ \PS\ nature of coronal
emission has implications for coronal seismology, and may be
indicative of the nature of the fundamental energy deposition that
keeps the corona hot.

@@

Hence, the number of effectively independent pixels time-series must
be calculated. {\bf The dependence of pixels on each other is
  calculated using the following modeling assumptions.}  First, a pair
of randomly chosen next-nearest neighbor pixels are selected from the
region.  Next nearest neighbor pixels are chosen as close physical
proximity is most likely to express the strongest interdependence.
Next, the cross correlation $c(\tau)$ function between two randomly
chosen next-nearest neighbor pixels is calculated.  The cross
correlation coefficient measures the linear dependence of two time
series $X(t)$ and $Y(t \pm \tau)$ at different lag {\bf times $\tau$.
  The assumption here is that the linear dependence as measured by the
  cross-correlation coefficient estimates the actual dependence
  between time-series.}  The cross correlation coefficient is used to
define a coefficient of independence between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  This
procedure is repeated 10,000 times.  For each value of $\rho$ found,
the effective number of pixels $N_{eff}$ is defined as
values is defined as
\begin{equation}\label{eqn:neff}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
where $\hat{\rho}$ is the arithmetic mean of the values of $\rho$
found.
